---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coronaaus

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-EmilySheehan0012/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-EmilySheehan0012/actions)
<!-- badges: end -->

The purpose of this package is to launch and simplify an app. The app is a tool which hopes to assist with the comparison and analysis of coronavirus in chosen states/territories in Australia. 

## Installation

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-EmilySheehan0012")
```
## Example

This example shows you how to launch the 'Coronavirus in Australia' app using the package:

```{r example-launch, eval = FALSE}
library(coronaaus)
coronaaus::launch_app()
```

This example shows you how to use the coronavirus data within the package:

```{r example-data}
head(coronaaus::corona_aus, 10)
```




